Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-24 ms.tex
quote typical delta(nu)/nu for Planck bandpasses
addressing various minor comments

\subsection{Pixelization}
\label{sec:pix}
For the purpose of fitting, we break the sky into $\sim$50 million pixels of 
angular size $\sim$1.72$'$, defined by the HEALPix pixelization in Galactic 
coordinates, with $N_{side}$=2048. This pixelization is convenient because it 
is the same format in which the \PLANCK~HFI maps were released, and because it 
adequately samples the $6.1'$ FWHM maps under consideration in our 
full-resolution fits. Our procedure will fit the intensity measurements in each
spatial pixel independently of those in neighboring pixels.

\subsection{Finite Bandpass Correction}
\label{sec:bpcorr}
The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
flux density $M_{\nu}$ in e.g. MJy/sr for any single frequency $\nu$. In 
practice, however, we wish to constrain our model using measurements in the 
broad \verb|i100|/\PLANCK~bandpasses, typically hundreds of GHz wide. We have 
therefore computed dimensionless finite bandpass correction factors to 
account for the MBB($T$, $\beta$) spectral shape and the transmission as a 
function of frequency:

@@

The resulting full-sky map of $f_1$ is shown in Figure \ref{fig:f1}. Some of 
the most striking features occurr near the north Galactic pole, and to 
highlight these regions of unusually high $f_1$, we display the northern
Galactic hemisphere in Lambert projection in Figure \ref{fig:f1lambert}.

@@

While the temperature and optical depth maps thus far derived are
useful for making thermal dust emission foreground predictions, estimating 
optical reddening/extinction is another important application of the 
$\tau_{545}$ map. We calibrate to reddening empirically rather than derive
a relationshp between $\tau_{545}$ and reddening by introducing additional 
assumptions about the dust grain physics and size distribution.

@@

Along with a library of stellar atmosphere models, the spectral lines of these
stars can be used to predict their intrinsic optical broadband colors. The 
`true' reddening is then simply the difference in the observed $g-r$ color and
the $g-r$ color predicted from the spectral lines. Applying a 
color transformation then yields `true' $E(B-V)$ values for $\sim$250,000 lines
of sight, mostly at high Galactic latitude. The calibration of two-component 
optical depth to $E(B-V)$ is then performed as a linear regression of 
$E(B-V)_{SSPP}$ versus $\tau_{545}$. $\tau_{545}$ is considered to the 
independent variable in this regression, as we ultimately wish to predict 
$E(B-V)$ as a function of optical depth, and $\tau_{545}$ has much higher S/N 
than the SSPP $E(B-V)$ estimates.

>>>>

\subsection{Pixelization}
\label{sec:pix}
For the purpose of fitting, we break the sky into $\sim$50 million pixels of 
angular size $\sim$1.72$'$, defined by the HEALPix pixelization in Galactic 
coordinates, with $N_{side}$=2048. This pixelization is convenient because it 
is the same format in which the \PLANCK~HFI maps were released, and because it 
adequately samples the $6.1'$ FWHM maps under consideration in our 
full-resolution fits. Our procedure will fit the intensity measurements in each
spatial pixel independently.

\subsection{Finite Bandpass Correction}
\label{sec:bpcorr}
The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
flux density $M_{\nu}$ in e.g. MJy/sr for any single frequency $\nu$. In 
practice, however, we wish to constrain our model using measurements in the 
broad \verb|i100|/\PLANCK~bandpasses, each with $\Delta\nu/\nu\sim0.3$. We 
have therefore computed dimensionless finite bandpass correction factors to 
account for the MBB($T$, $\beta$) spectral shape and the transmission as a 
function of frequency:

% is delta(nu)/nu conventionally (nu_off-nu_on)/nu_c or 1/2 of that ?

@@

The resulting full-sky map of $f_1$ is shown in Figure \ref{fig:f1}. Some of 
the most striking features occur near the north Galactic pole, and to 
highlight these regions of unusually high $f_1$, we display the northern
Galactic hemisphere in Lambert projection in Figure \ref{fig:f1lambert}.

@@

While the temperature and optical depth maps thus far derived are
useful for making thermal dust emission foreground predictions, estimating 
optical reddening/extinction is another important application of the 
$\tau_{545}$ map. We calibrate to reddening empirically rather than derive
a relationship between $\tau_{545}$ and reddening by introducing additional 
assumptions about the dust grain physics and size distribution.

@@

Given a library of stellar atmosphere models, the spectral lines of these stars
can be used to predict their intrinsic optical broadband colors. The `true' 
reddening is then simply the difference in the observed $g-r$ color and the 
$g-r$ color predicted from the spectral lines. Applying a color transformation 
then yields `true' $E(B-V)$ values for $\sim$250,000 lines of sight, mostly at 
high Galactic latitude. The calibration of two-component optical depth to 
$E(B-V)$ is then performed as a linear regression of $E(B-V)_{SSPP}$ versus 
$\tau_{545}$. $\tau_{545}$ is considered to be the independent variable in this
regression, as we ultimately wish to predict $E(B-V)$ as a function of optical 
depth, and $\tau_{545}$ has much higher S/N than the SSPP $E(B-V)$ estimates.
